---
title: "Hexagon Mapping Test"
author: "JBailey"
date: "19 October 2016"
output: html_document
---

```
#I wanted to create something that would turn any shapefile / geojson into a hexagonal map where each geographical unit (e.g. states) becomes a hexagon. 

I need to optimise the assignment algorithm. 
I need to optimise the grid size algorith. At the moment they're both greedy and lazy on my part. 

```

```{r setup, include=FALSE}
library(RColorBrewer) #to use brewer.pal
library(fields) #to use designer.colors
```

- Read in geofile
- Get extent of geofile
- Specify required number of hexagons needed based on number of units in geofile. 
- Generate grid of number of points needed within the boundary of the geofile.
- Assign centroid of original units to closest point in grid (remove that point)
- Repeat until all centroids are assigned to points. 
- Add hexagons around points. 
- Plot and colour accordingly. 

```{r, eval=FALSE}
library(rgdal)
library(maptools)
library(sp)
library(rgeos)

prefix = "../data/"
filename = "London_LA"
f_type = "geojson"
#f_type = "shapefile"


if (f_type == "shapefile"){
    shape <- readOGR(paste0(prefix,filename))
} else {
  shape <- readOGR(paste0(prefix,filename,".json") , "OGRGeoJSON") }

shape@proj4string <- CRS(as.character(NA))

#function find suitable cellsize
nhex <- length(shape)

#Start off with guidance but start with bins that are too large (cellsize too large)
xmax <- summary(shape)[2][[1]][1,2]
ymax <- summary(shape)[2][[1]][2,2]
xmin <- summary(shape)[2][[1]][1,1]
ymin <- summary(shape)[2][[1]][2,1]
xrange <- (xmax - xmin)
yrange <- (ymax - ymin)
start_width <- ifelse(xrange > yrange, xrange, yrange)

#Let's assume that the user want's something more than 4 hexagons wide or long.
#If they want something this small then a hexmap is probably not worth it.
cellsize = start_width / 4
#At what cellsize is there the correct number of hexagons?
#TODO: this really should be re-framed as an optimisation. 
  repeat {
    # do something
    HexPts <- spsample(shape, type="hexagonal", cellsize=cellsize) 
    cellsize = ifelse(abs(nhex - length(HexPts)) > 200, cellsize*0.9,
                      ifelse(abs(nhex - length(HexPts)) < 10, cellsize*0.999999999999, cellsize*0.999))
    print(cellsize)
    print(paste0("Needed = ", nhex))
    print(paste0("Current = ", length(HexPts)))
    print(paste0("Difference ", abs(nhex - length(HexPts))))
    # exit if the condition is met
    if (abs(nhex - length(HexPts)) < 2){
      print(paste0("We're close We Need ", nhex, " we have ", length(HexPts), " Cellsize is ", cellsize))}
    
    if (nhex < length(HexPts)) {
       HexPts <- spsample(shape, type="hexagonal", cellsize=cellsize) 
       cellsize = cellsize*1.00000000001
    }
    if (nhex == length(HexPts)) break
  }

#TODO: If the Current Exceeds Needed then Stop. Rotate By 1 degree. And go down from where you are in very small increments. 

HexPols <- HexPoints2SpatialPolygons(HexPts)
plot(HexPols[shape,])


```


Assign the New Hexagons to Their Closest Actual Units

```{r, eval = FALSE}
# Latest version: Assign closest points from a second point set

   require(sp)
   
   originalPoints <- gCentroid(shape,byid=TRUE)  
   shape@data$CENTROIX <- originalPoints$x
   shape@data$CENTROIY <- originalPoints$y
   shape@data$key <- paste0(originalPoints$x, originalPoints$y)

   hexagonPoints <- HexPts
   HexPts2 <- as.data.frame(HexPts)
   hexdfid <- rep("NA", times = nhex)
   for (i in 1:nhex) {hexdfid[i] <- paste0("ID", i)}
   row.names(HexPts2) <- hexdfid
   hexpolsdf <- SpatialPolygonsDataFrame(HexPols, data = HexPts2)

   hexpolsdf@data$key2 <- paste0(hexpolsdf@data$x, hexpolsdf@data$y)
   #validOrigPoints <- originalPoints

#  Define these vectors, used in the loop.

   closestSiteVec <- vector(mode = "numeric",length = length(hexagonPoints))
   minDistVec     <- vector(mode = "numeric",length = length(hexagonPoints))
   takenVec       <- vector(mode = "numeric",length = length(hexagonPoints))
   takenVecIndex <- vector(mode="numeric", length=0) 

   
#If we want to prioritise this by area then we need to know the area of each shape.
sapply(shape@polygons, function(x) x@area)

## For areas, rgeos::gArea() or geosphere::areaPolygons() are generally more appropriate
## (Note, for instance, that it properly accounts for the hole in the 3rd polygon.)
sizes <- rgeos::gArea(shape, byid=TRUE)

# Get the vector index of the hexagon centroid closest to each original centroid.
# Use the spDistsN1 function to compute the distance vector between each
# original centroid and all of the hexagon centroids. Then, find and
# retain the index of the closest hexagon centroid. 
#
# spDistsN1 usage: spDistsN1(pointList, pointToMatch, longlat)
#
# where:
#         pointList   : List of candidate points.
#         pointToMatch: Single point for which we seek the closest point in pointList.
#         longlat     : TRUE  computes Great Circle distance in km,
#                       FALSE computes Euclidean distance in units of input geographic coordinates
#
# We could use Great Circle distance to increase distance calculation accuracy at high latitudes
#
#TODO: Order from smallest to largest. Or randomised.  Or miimise total distance.   
plan = "sm"
#plan = ""
     
   for (i in 1 : length(hexagonPoints))
   {
     
     if (plan == "sm") {i <- order(sizes)[i]}
       
       
      distVec <- spDistsN1(originalPoints,hexagonPoints[i,],longlat = FALSE)
      minDistVec[i] <- min(distVec)
      
      if (i > 1){
              distVec[takenVecIndex] <- NA
              closestSiteVec[i] <- which.min(distVec)
      } else {closestSiteVec[i] <- which.min(distVec)}
      
      takenVec[i] <- which.min(distVec)
      takenVecIndex <- takenVec[takenVec > 0]
   }
   
   print(takenVecIndex)

   PointAssignTemps <- originalPoints[closestSiteVec,]
   FinalTable = data.frame(coordinates(hexagonPoints), closestSiteVec,minDistVec,PointAssignTemps)

   names(FinalTable) <- c("HexagonX","HexagonY","ClosestSiteVec","MinDist","CENTROIDX", "CENTROIDY")
   FinalTable$key <- paste0(FinalTable$CENTROIDX, FinalTable$CENTROIDY)
   combi <- merge(shape@data, FinalTable, by = "key")
   combi$key2 <- paste0(combi$HexagonX, combi$HexagonY)
   combi2  <- merge(hexpolsdf, combi, by = "key2")

   
#Generate colours for the test plotting
   tombolocs <- c("#ff15a3","#cccccc","#85daef","#006dfe","#0257c5")
   rbpal <- colorRampPalette(tombolocs)
   
#Run a comparison test plot with two columns. 
   par(mfrow=c(1,2))
   plot(shape, col = rbpal(16)[as.numeric(cut(shape$HECTARES,breaks = 10))], border = NA, main = "Areas" )
   text(x = combi2$CENTROIDX, y = combi2$CENTROIDY, labels = combi2$NAME, cex = 0.5)
   plot(combi2, col = rbpal(16)[as.numeric(cut(combi2$HECTARES,breaks = 10))], border = NA, main = "Areas")
   text(x = combi2$HexagonX, y = combi2$HexagonY, labels = combi2$NAME, cex = 0.5)
   
```
